CNNNano --- MinION basecaller pogonjen dubokim ucenjem

### 2017-04-28 paper/main.tex
Added nanocall into paper
Changed abstract

\begin{sazetak}
TODO: ovo je pre-alpha draft...bude se vec osvjezilo

\kljucnerijeci{planiranje nabave, stohastička potražnja, optimalna količina nabave, Model dinamičke ekonomske količine nabave}
\end{sazetak}

\begin{abstract}
    The MinION device by Oxford Nanopore is the first portable sequencing device. MinION is able to produce very long reads (reads over 100 kBp were reported), however it suffers from high sequencing error rate. In this paper, we show that the error rate can be reduced by improving the base calling process using residual convolutional neural networks(CNN) combined with Connectionist Temporal Classification (CTC).
\keywords{procurement planning, dynamic lot sizing model, stochastic demands}
\end{abstract}

>>>>

\begin{sazetak}
TODO

\kljucnerijeci{TODO}
\end{sazetak}

\begin{abstract}
    The MinION device by Oxford Nanopore is the first portable sequencing device. MinION is able to produce very long reads (reads over 100 kBp were reported), however it suffers from high sequencing error rate. In this paper, we show novel model reducing the error rate can be reduced by improving the base calling process using gated residual convolutional neural networks (CNN) combined with Connectionist Temporal Classification (CTC) learning approach.
\keywords{procurement planning, dynamic lot sizing model, stochastic demands}
\end{abstract}
